Detecting Stylistic Variation in Pop Production

### 2023-11-22 outputs/paper/paper.qmd
more editz

```{r}
#| label: fig-dancevariance
#| echo: false
#| warning: false
# Danceability Plot

@@

ggplot(selected_data, aes(x=term, y=danceability, fill=producer)) +
  geom_bar(stat="identity", position="dodge") +
  labs(title="Danceability across Producers", y="Danceability Score", x= "Feature") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

```{r}
#| label: fig-dancevariance
#| fig-cap: Danceability Scores Across Producers
#| echo: false
#| warning: false
# Danceability Plot

@@

ggplot(selected_data, aes(x=term, y=danceability, fill=producer)) +
  geom_bar(stat="identity", position="dodge") +
  labs(y="Danceability Score", x= "Feature") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
